Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-23 paper.tex
Updated Experiments
Rosenbrock Function now included.

>>>>

\subsubsection{Rosenbrock Benchmark Function Experiment}

    \begin{figure}
        \includegraphics[width=\linewidth, frame]{img/fig_fun_rosenbrock_5d.pdf}
        \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 5 Dimensions.} \label{fig.fun_rosenbrock_5d}
        \end{figure}

    \begin{figure}
        \includegraphics[width=\linewidth, frame]{img/fig_fun_rosenbrock_10d.pdf}
        \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 10 Dimensions.} \label{fig.fun_rosenbrock_10d}
        \end{figure}
